Is It Possible to Steal Money Through USB-C?

### 2020-12-29 WOOT/Files/experiment.tex
experiment case study

\section{Experiment}
\label{sec:experiment}
\noindent\outline{Case Study: Sharing Power Bank}\\
\outline{Overview}\\
\outline{Attack Procedure(how to  get picture, etc.)}\\
\outline{Security Issues against APPLE/Android...etc.}\\
Overview, the experiment equipment consists of
a USB Type-C hub with HDMI and USB port,
a raspberry pi 4B with a Wi-Fi chip onboard,
a video capture card adapting HDMI signal to USB camera,
and a normal powerbank with dual outputs.

>>>>

\section{Experiment}
\label{sec:experiment}
\noindent\outline{Case Study: Sharing Power Bank}\\

\subsection{Case study: Power Bank Sharing}

Power bank sharing is a digital service which allows user to take short term rentals of power banks. A common service provider deploys a large number of power bank sites in the city. Then, users can rent power banks from any of the power bank sites, charge their device on the trip, return rented power banks to any of the power bank sites, and pay rent online.

\yechang{site or repository? }

As an example, Brick is such a power bank sharing service provider from Swidian.

\yechang{add hyperlink or reference to Brick or Brick App on app store/googleplay.}

\yechang{Add more example to show that it is widely used?}
It provides convenience for users, but it also brings security risks. We notice that the power bank site does not check the integrity of the power bank during the rental process of the power bank, and users are hardly alert when connecting their devices to the power bank. In some situations, a malicious user is able to do some tricks to a rented power bank, return it to a power bank site as normal, and its next user will unknowingly connect to a malicious power bank, which endangers the data and privacy security in users' device.

\outline{Overview}\\

\subsection{Overview}

\outline{Attack Procedure(how to  get picture, etc.)}\\
\outline{Security Issues against APPLE/Android...etc.}\\
Overview, the experiment equipment consists of
a USB Type-C hub with HDMI and USB port,
a raspberry pi 4B with a Wi-Fi chip onboard,
a video capture card adapting HDMI signal to USB camera,
and a normal powerbank with dual outputs.
